The Importance of Affective States in Privacy Calculus

### 2021-05-03 submission.tex
password security rephrase

\subsection{Password Security}
There exists a strong relationship such that \emph{if an individual used the
same passwords for most of their accounts, they feel worse about it if they use
some password protective measures}. The gamma value of this relationship is
.477, with p<.05 (*). Despite the strength of the relationship, the Chi-Square
p-value of .131 indicates that the null hypothesis cannot be ruled out.

>>>>

\subsection{Password Security} \label{Password Security}
There exists a strong relationship such that \emph{the worse an individual feels
if they used the same passwords for most of their accounts, the more likely they
are to use password protective measures}.  The gamma value of this relationship
is .477, with p<.05 (*). Despite the strength of the relationship, the
Chi-Square p-value of .131 indicates that the null hypothesis cannot be ruled
out.
